---
title: "Demo: Editor Options"
format: 
  html:
    fontsize: "80%"
engine: knitr
webr:
  cell-options:
    editor-font-scale: 0.95
filters:
  - webr
---

:::{.callout-important}
These features are currently experimental and are included in the 0.4.2-dev.2 build of `{quarto-webr}`.
:::

# Overview

This feature demo introduces new options for styling the interactive editor associated with `{webr-r}` code blocks. These editor-specific options offer greater flexibility when working with the Monaco Editor integrated into the interactive area.

:::{.callout-note}
These options are only configurable during the document authoring stage.
:::

## `editor-font-scale` Option

The editor area now inherits font size from Quarto's `fontsize` theme option, ensuring consistency with other elements on the page. You can adjust the font size for the editor relative to Quarto's output by setting the `editor-font-scale` option. When `editor-font-scale` is:

- Equal to 1 (`= 1`), the editor's font size matches the `fontsize` value.
- Less than 1 (`< 1`), the editor's font size is smaller than the `fontsize` value.
- Greater than 1 (`> 1`), the editor's font size is larger than the `fontsize` value.

### Default Size

By default, we set `editor-font-scale` to 1, aligning the editor font size with the `fontsize` value.

Let's consider a standard code cell that fits a linear model and obtains the confidence intervals for one or more parameters in a fitted model:

```{r}
#| echo: true
fit = lm(mpg ~ am, data = mtcars)

confint(fit)
```

Now, let's observe the effect with `editor-font-scale: 1`:

```{webr-r}
#| autorun: true
#| editor-font-scale: 1
fit = lm(mpg ~ am, data = mtcars)

confint(fit)
```

Notice the consistency in font sizes.

### Reducing Editor Size

To decrease the font size, we set a value between `0 < editor-font-size < 1`. For example, let's set `editor-font-scale` to 0.5:

```{webr-r}
#| autorun: true
#| editor-font-scale: 0.5
fit = lm(mpg ~ am, data = mtcars)

confint(fit)
```

### Increasing Editor Size

To increase the font size, we set a value between `editor-font-size > 1`. For example, let's set `editor-font-scale` to 2:

```{webr-r}
#| autorun: true
#| editor-font-scale: 2
fit = lm(mpg ~ am, data = mtcars)

confint(fit)
```

### Scaling Content Areas

In this example, we create a custom area using a [Div block in Quarto](https://quarto.org/docs/authoring/markdown-basics.html#sec-divs-and-spans) and set the div's font size to 150%. Consequently, the editor inherits the font size within the area.

:::  {.panel-tabset group="scaledEditor"}
#### `{quarto-webr}` Output
::: {#big-text style="font-size: 150%"}

##### Quarto code cell for R

```{r}
#| echo: true
fit = lm(mpg ~ am, data = mtcars)

confint(fit)
```

##### webR code cell under quarto-webr

```{webr-r}
#| autorun: true
fit = lm(mpg ~ am, data = mtcars)

confint(fit)
```
:::

#### Cell Code
````md

::: {#big-text style="font-size: 150%"}

Quarto code cell for R

```{r}
#| echo: true
fit = lm(mpg ~ am, data = mtcars)

confint(fit)
```

webR code cell under quarto-webr

```{webr-r}
#| autorun: true
fit = lm(mpg ~ am, data = mtcars)

confint(fit)
```
:::

````
:::

# Fin

Just the beginning!