---
title: webR in Quarto HTML Documents
format: 
#  html: default
#  revealjs: default
  html:
    fontsize: "80%" 
  revealjs:
    fontsize: 30
    css: adjust-revealjs.css
engine: knitr

webr:
  celldefaults:
    out-width: "100%"
    font-scale: 0.95

filters:
  - webr
    
---

Here is an ordinary code cell demonstrating `confint.lm`.
Revealjs scales content down to `0.55 em`. Perhaps this should be emulated for qwebr-editor cells? I actually don't like it... Added an extra css for adjusting back to `1 em`.
```{r}
#| echo: true
fit = lm(mpg ~ am, data = mtcars)

confint(fit)
```


This is a webR-enabled code cell in a Quarto HTML document, with autorun (👍 to autorun!). Another option would be that the editor div inherits font size from quartos output. Then font-scale is relative to that one.

```{webr-r}
#| autorun: true
fit = lm(mpg ~ am, data = mtcars)

confint(fit)
```  

## Now in a div with scaling

In the following paragraph, font size is set to 150%. This affects R code cells.

::: {#bigman style="font-size: 150%; color: green;"}
Ordinary code cell
```{r}
#| echo: true
fit = lm(mpg ~ am, data = mtcars)

confint(fit)
```

Quarto webr
```{webr-r}
#| autorun: true
fit = lm(mpg ~ am, data = mtcars)

confint(fit)
```
:::